\chapter{Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Background}
The MSc project should address the following:
\begin{itemize}
\item Analysis of environmental challenges, both natural and artificial affecting the reliability of computer vision systems, both for fixed rigs and dynamic vessels with real-world images for description.
\item Analysis of various computer vision sensor technologies and their suitability in the offshore environment.
\item Description and cost-to-benefit analysis of potential applications in pipe handling equipment coupled with computer vision.
\item Analysis of commercial products trying to solve aforementioned challenges.
\item Analysis of case study implementation, Glyph-tracking of equipment using a PTZ camera.
\end{itemize}

An implementation of the case study will also be presented, allowing automatic camera tracking of equipment to free up hands and improve visual feedback to supervisors.
\paragraph{Objectives}
\begin{enumerate}
  \item Determine and evaluate challenges and possible solutions for the offshore industry to use computer vision.
  \item Implement a case study of an automated CCTV camera.
\end{enumerate}


\paragraph{Structure of the report}
All the software developed as a part of this project can be found at the authors personal repository at Github ~\cite{Github}, feel free to use this for future work.

\paragraph{Structure of the CD}
The CD contains a snapshot of the latest Github code repository as of the date of this report.