\subsection*{Preface}
\addcontentsline{toc}{subsection}{Preface}
This master thesis is submitted in partial fulfilment of the requirements for the degree MSc. in Engineering Cybernetics at the Norwegian University of Science and Technology.

The motivation has been to study the feasibility of using computer vision offshore, and follow this up with an implementation of a potential application, hopefully aiding in increased safety and reduced cost of operations.

The motivation for this work has been to implement an automated CCTV system for tracking machines that are in motion, improving upon work previously done in the field. By visually following machines, I hope this work will lead to improved safety and productivity in the industry. Part of this thesis will also look into increasing reliability of control systems that are managing drill pipes on an oil rig.

I would like to thank my supervisor Professor Tor Onshus from NTNU and co-supervisor Doctor Mads Hvilshøj from MHWirth AS for their guidance and support throughout the project.

I would also like to thank Omega Verksted for their support when I needed to bounce programmatic ideas and build parts of the test setup, and also for supplying an abundance of coffee and pictures of cute kittens when I needed it the most.

No work would be complete unless I also thanked NTNUI Dykkergruppa, a student organization that has been much like a family to me through my years at the university. Without their support, I would probably never have finished my degree.

Thank you.

\blfootnote{Keywords: computer vision, offshore, extreme environment, decision support, motion tracking, cctv, drilling vessel, oil \& gas, drilling applications, machine vision, opencv }
\newpage
